Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-06-05 Manuscript/main.tex
Fixing pgls table legend.

\begin{landscape}
\begin{table}[ht]
\centering
\begin{tabular}{rrllllllllrr}
  \hline
 Model & $E_{species}$ & $I_{species}$ & $E_{clade}$ & $I_{clade}$ & $E_{species}$ x $I_{clade}$ & $E_{species}$ x $E_{clade}$ & $I_{species}$ x $I_{clade}$ & $I_{species}$ x $E_{clade}$ & delta AIC & Adj. R2 \\ 
  \hline
1 & 0.04*** & -0.139*** & 0.002 & -0.002 & 0.064*** & 0.045*** & 0.341*** & 0.093*** & 0.00 & 0.92 \\ 
2 & 0.257*** & 0.169*** & 0.01 & 0.001 & 0.045*** &  & 0.312*** & 0.034*** & -691.48 & 0.92 \\ 
3 & 0.108*** & 0.236*** & 0.012 & -0.002 & 0.055*** & 0.034*** & 0.343*** &  & -284.74 & 0.92 \\ 
4 & 0.254*** & 0.104*** & 0.002 & 0.004 &  & 0.027*** & 0.311*** & 0.052*** & -877.85 & 0.92 \\ 
5 & 0.1*** & 0.571*** & -0.018* & 0.02*** & 0.054*** & 0.036*** &  & 0.096*** & -1498.36 & 0.91 \\ 
6 & 0.364*** & 0.973*** & -0.007 & 0.023*** &  &  &  &  & -2230.10 & 0.90 \\ 
7 & 0.364*** & 0.972*** &  &  &  &  &  &  & -2280.08 & 0.90 \\ 
8 &  &  & -0.025 & 0.011 &  &  &  &  & -22270.55 & -0.00 \\ 
9 & 0.286*** &  &  &  &  &  &  &  & -18986.63 & 0.32 \\ 
10 &  & 0.798*** &  &  &  &  &  &  & -17714.99 & 0.41 \\ 
11 &  &  & -0.008 &  &  &  &  &  & -22269.34 & -0.00 \\ 
12 &  &  &  & 0.002 &  &  &  &  & -22269.51 & -0.00 \\ 
   \hline
\end{tabular}
\caption{Elaboration and innovation as predictors of beak shape distance from centroid.
The table shows parameter estimates of predictors from  13 different phylogenetic generalised least squares (PGLS) models with $\Delta$AIC showing relative model fit following removal of terms. Models 1-6 are multiple regressions including all variables and one or more interaction terms; models 7-9 are are multiple regressions including two or more variables and no interaction terms; models 10-13 are single predictor models. Values in the table are based on PGLS in which Pagel’s $\lambda$ was fixed at 1 (i.e. assuming a Brownian motion model of evolution). Fixing $\lambda$ is necessary to allow model comparison with AIC. We also fitted the same models fixing $\lambda$ to 0.727 (the lowest value of $\lambda$lambda from any individual model) and relative model fit and interpretation of parameters was unaffected. E = elaboration; I = innovation; AIC = Akaike Information Criterion; NS = not significant; - indicates that the term was not included within that model.}
\label{Tab:pgls}
\end{table}
\end{landscape}

>>>>

\begin{landscape}
\begin{table}[ht]
\centering
\begin{tabular}{rrllllllllrr}
  \hline
 Model & $E_{species}$ & $I_{species}$ & $E_{clade}$ & $I_{clade}$ & $E_{species}$ x $I_{clade}$ & $E_{species}$ x $E_{clade}$ & $I_{species}$ x $I_{clade}$ & $I_{species}$ x $E_{clade}$ & $\Delta$AIC & Adj. $r^2$ \\ 
  \hline
1 & 0.04*** & -0.139*** & 0.002 & -0.002 & 0.064*** & 0.045*** & 0.341*** & 0.093*** & 0.00 & 0.92 \\ 
2 & 0.257*** & 0.169*** & 0.01 & 0.001 & 0.045*** &  & 0.312*** & 0.034*** & -691.48 & 0.92 \\ 
3 & 0.108*** & 0.236*** & 0.012 & -0.002 & 0.055*** & 0.034*** & 0.343*** &  & -284.74 & 0.92 \\ 
4 & 0.254*** & 0.104*** & 0.002 & 0.004 &  & 0.027*** & 0.311*** & 0.052*** & -877.85 & 0.92 \\ 
5 & 0.1*** & 0.571*** & -0.018* & 0.02*** & 0.054*** & 0.036*** &  & 0.096*** & -1498.36 & 0.91 \\ 
6 & 0.364*** & 0.973*** & -0.007 & 0.023*** &  &  &  &  & -2230.10 & 0.90 \\ 
7 & 0.364*** & 0.972*** &  &  &  &  &  &  & -2280.08 & 0.90 \\ 
8 &  &  & -0.025 & 0.011 &  &  &  &  & -22270.55 & -0.00 \\ 
9 & 0.286*** &  &  &  &  &  &  &  & -18986.63 & 0.32 \\ 
10 &  & 0.798*** &  &  &  &  &  &  & -17714.99 & 0.41 \\ 
11 &  &  & -0.008 &  &  &  &  &  & -22269.34 & -0.00 \\ 
12 &  &  &  & 0.002 &  &  &  &  & -22269.51 & -0.00 \\ 
   \hline
\end{tabular}
\caption{Elaboration and innovation as predictors of beak shape distance from centroid.
The table shows parameter estimates of predictors from  12 different phylogenetic generalised least squares (PGLS) models with $\Delta$AIC showing relative model fit following removal of terms. Models 1-5 are multiple regressions including all variables and one or more interaction terms; models 6-8 are are multiple regressions including two or more variables and no interaction terms; models 9-12 are single predictor models. Values in the table are based on PGLS in which Pagel’s $\lambda$ was fixed at 1 (i.e. assuming a Brownian motion model of evolution). Fixing $\lambda$ is necessary to allow model comparison with AIC. We also fitted the same models fixing $\lambda$ to 0.727 (the lowest value of $\lambda$lambda from any individual model) and relative model fit and interpretation of parameters was unaffected. E = elaboration; I = innovation; AIC = Akaike Information Criterion; NS = not significant; - indicates that the term was not included within that model.}
\label{Tab:pgls}
\end{table}
\end{landscape}
